\begin{thebibliography}{00}
\bibitem{b2} Martino, J., \& Setters, D. (2020, July 27). Precision Motors help guided parachutes deliver cargo. Tech Briefs. \url{https://www.techbriefs.com/component/content/article/tb/supplements/mct/features/applications/11837}

\bibitem{b3} Precision guided parachutes - maxongroup.us. Available at: \url{https://www.maxongroup.us/medias/sys_master/root/8803679404062/Precision-Guided-Parachutes.pdf?attachment=true} (Accessed: 01 July 2023).

\bibitem{b11} Ultra-Wideband RTLS, Positioning, \& Sensor Technology Available at: \url{https://www.inpixon.com/technology/standards/ultra-wideband#:~:text=What%20is%20the%20Range%20of,sight%20between%20devices%20or%20anchors.} (Accessed: 07 September 2023). 

\bibitem{b8} La velocità di un paracadutista con un paracadute aperto. Velocità di caduta del paracadutista. (no date) Kemtalant. Available at: \url{https://kem-talant.ru/it/bodybuilding/skorost-parashyutista-s-raskrytym-parashyutom-skorost.html} (Accessed: 21 August 2023). 

\bibitem{b9} La dimensione del paracadute. (no date) Kemtalant. Available at: \url{https://www.sportsrec.com/7305468/the-size-of-skydiving-parachutes} (Accessed: 21 August 2023). 

\bibitem{b7} Britannica, The Editors of Encyclopaedia. "parachute". Encyclopedia Britannica, 7 Aug. 2023, \url{https://www.britannica.com/technology/parachute}. Accessed 21 August 2023.

\bibitem{b10} F.A.Q. | Skydive Lucca (no date) Scuola di paracadutismo Lucca. Available at: \url{http://www.paracadutismolucca.it/f-a-q/} (Accessed: 21 August 2023). 

\bibitem{b12} Kim, Y., \& Bang, H. (2019). Introduction to Kalman Filter and Its Applications. IntechOpen. doi: 10.5772/intechopen.80600

\bibitem{b1} Manuel Boldrer, Luigi Palopoli, Daniele Fontanelli,
A unified Lloyd-based framework for multi-agent collective behaviours,
Robotics and Autonomous Systems,
Volume 156,
2022,
104207

\bibitem{b15} S. Ahmad and M. O. Tokhi, "Linear Quadratic Regulator (LQR) approach for lifting and stabilizing of two-wheeled wheelchair," 2011 4th International Conference on Mechatronics (ICOM), Kuala Lumpur, Malaysia, 2011, pp. 1-6, doi: 10.1109/ICOM.2011.5937119.

\bibitem{b5} Benhabib, B. \& Goldenberg, Andrew A. \& Fenton, R.. (2007). A Solution to the Inverse Kinematics of Redundant Manipulators. Journal of Robotic Systems. 2. 373 - 385. 10.1002/rob.4620020404. 

\bibitem{b6} Aristidou, A. \& Lasenby, J. Inverse kinematics: a review of existing techniques and introduction of a new fast iterative solver. (University of Cambridge, Department of Engineering,2009)

\bibitem{b4} İşleyen, A., Wouw, N. \& Arslan, Ö. Feedback Motion Prediction for Safe Unicycle Robot Navigation.  (2023)

\bibitem{b13} Daniele Fontanelli,
Notes of the course "Intelligent distributed systems",
2022/2023

\bibitem{b14} S. S. Kia, S. Rounds and S. Martinez, "Cooperative Localization for Mobile Agents: A Recursive Decentralized Algorithm Based on Kalman-Filter Decoupling," in IEEE Control Systems Magazine, vol. 36, no. 2, pp. 86-101, April 2016, doi: 10.1109/MCS.2015.2512033.
\end{thebibliography}
%\renewcommand*{\bibfont}{\normalfont\tiny}
% Print bibliography
%{
%\tiny
%\printbibliography
%}